Circular Regression Trees and Forests with an Application to Probabilistic Wind Direction Forecasting

### 2020-07-05 pkg/circtree/inst/wind_paper/draft/JRSSC/rebuttal.tex

Due to the COVID-19 pandemic our response took us longer than planned but
we have finally carefully revised our manuscript, incorporating the feedback
and suggestions. The most substantial changes in the manuscript are the following:

\begin{itemize}
\item We have fully revised the `Abstract' giving more emphasis to the application.
In addition, we now use the term `application' instead of `case study' throughout
the manuscript and have also renamed Sect.~4 accordingly.

\item In the section `Computational details', we have added information about the
order of magnitude of the computing time for the different methods on a standard desktop computer.

\item We now discuss the work of Hara and Chellappa~(2017) in relation to our
circular distributional trees within Sect.~1.1.

@@

First of all we want to thank you for your positive feedback and valuable input.

A very good remark, indeed split variable selection based on BIC creates an
alternative possible tree-building strategy. Per default when building a
circular distributional tree, the package \textbf{circtree} uses
\emph{p}-values from association tests both for selecting the split variable
and for a so-called pre-pruning strategy which stops growing the tree as soon
as no significant associations can be found in a given subgroup. However, as
discussed in Zeileis~\emph{et al.}~(2008), an alternative strategy is to use
information criteria such as AIC (Akaike information criterion) or BIC (Bayes
information criterion) for cost-complexity post-pruning, where a large tree is
first built and then pruned back. We now discuss post-pruning in the Appendix~A
of the manuscript and also refer to the submitted manuscript by
Schlosser~\emph{et al.}~2019, which investigates the performance of different
testing and pruning strategies employed in unbiased recursive partitioning
algorithms.

\vspace{0.5em}
\begin{re}
I would like to point out related works on circular regression models for
shape representation (Kashyap and Chellappa) and circular random forests for
vehicle direction estimation (Hara and Chellappa) given below. I feel there is
some overlap between this paper and the work of Hara and Chellappa on using
circular statistics for vehicle orientation estimation. The authors may include
some comparisons with Hara, Chellappa work.
\end{re}

Thank you very much for pointing out these interesting references that, unfortunately,
we were not aware of before. We now briefly discuss the work of Hara and Chellappa~(2017),
comparing their approach to ours in Sect.~1.1. The main difference is that their
algorithm aims at conditional mean estimation for circular data and only adopts
distributional aspects for determining the number of splits. Specifically, the
variances are restricted to be shared across splits whereas in our proposal they
are full model parameters estimated and tested along with the means.

### 2020-07-05 pkg/circtree/inst/wind_paper/draft/JRSSC/rebuttal.tex

\begin{re}
This is a well-written paper on using circular regression trees for analyzing a
specific type of circular data. The probabilistic approach is well-founded. The
experiments on wind direction data are well organized and the results are
thoroughly analyzed.
\end{re}

\begin{re}
The authors could address model order determination problem using the
Bayes Information Criterion (Schwartz, 1978, Annals of Statistics).  
\end{re}

First of all we want to thank you for your positive feedback and valuable input.

Indeed, information criteria like AIC or BIC are natural candidates for
determining the model order in distributional models, i.e., the number of splits
in distributional trees. While they could be used instead of the $p$-values in
the ``internal stopping'' or ``pre-pruning'', they are typically considered
for ``post-pruning'' after initially growing a large tree (e.g., in
Su~\emph{et al.}~2004 or Zeileis~\emph{et al.}~2008). This is now discussed
in Appendix~A along with the other details of the tree algorithm employed.
There we also refer to the recent work of Schlosser~\emph{et al.}~2019
which empirically investigates the performance of different pre- and post-pruning
strategies in unbiased recursive partitioning. This work finds that post-pruning
only improves the performance of the unbiased trees considered when the
underlying tests do not work well, e.g., when the power of the tests is low
or the sample size extremely large.

### 2020-07-05 pkg/circtree/inst/wind_paper/draft/draft.Rnw
shift post-pruning discussion to the end of the appendix and rephrase; adapted response to reviewer 2 correspondingly
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@3049 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: a8deb148eb7ff01dca120b567ab2e4c139a72526

An alternative split variable selection strategy is provided by cost-complexity
``post-pruning'', where a large tree is first built and then pruned back based
on the predictive performance \citep{Breiman+Friedman+Stone:1984}. As discussed
in \citet{Zeileis+Hothorn+Hornik:2008}, for model-based partitioning by
employing information criteria such as AIC~(Akaike information criterion) or
BIC~(Bayes information criterion) this strategy can be built on the same
underlying loss function as pre-pruning. However,
\citet{Schlosser+Hothorn+Zeileis:2019} show that post-pruning in an unbiased
tree algorithm is usually only superior to pre-pruning when the underlying
significance tests have low power, for example, due to a large data set.

@@

Subsequently, the same testing and splitting procedure is repeated in each of
the resulting subgroups until some stopping criterion is reached. Next to the
already mentioned significance-level-based stopping criterion, i.e., a minimal
$p$-value for the statistical tests, also a maximal tree depth or a minimal
number of observations in a node can be employed as stopping criteria.

>>>>

@@

Subsequently, the same testing and splitting procedure is repeated in each of
the resulting subgroups until some stopping criterion is reached. Complementing
the pre-pruning mentioned above, based on the significance level of the
statistical tests, further criteria such as maximal tree depth or a minimal
number of observations in a node can be employed.

In addition to, or as an alternative to, pre-pruning, classical post-pruning
can also be applied where a large tree is grown first and then pruned back based
on the predictive performance \citep{Breiman+Friedman+Stone:1984}. As pointed out
by \citet{Zeileis+Hothorn+Hornik:2008}, information criteria such as AIC~(Akaike
information criterion) or BIC~(Bayes information criterion) are natural candidates
for this when partitioning maximum likelihood models. However,
\citet{Schlosser+Hothorn+Zeileis:2019} show empirically that post-pruning only improves
upon pre-pruning in an unbiased tree algorithm when the underlying significance
tests do not work well, e.g., when they have low power or when the number of observations
is extremely large.
